A free/open-source machine translation system for English to Kazakh

### 2015-01-22 engkaz-eamt-2015/engkaz-eamt-2015.tex
bilingual dictionary
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58532 72bbbca6-d526-0410-a7d9-f06f51895060

Kazakh dictionary uses
\section{Results}

>>>>

Bilingual dictionary provides correspondences between lexical forms of source and target lanugages. Each entry consists of English word on the left side with part of speech and corresponding Kazakh word on the right side. Some entries could be ambiguous by part of speech, or just have many translations, which wil be chosen by lexical selection rules depend on context. This dictionary currently contains 13130 stems.

\section{Results}
